---
title: "Space-use of birds in the Basel Zoo"
author: "Master by Tabea Jandt"
date: "12.04.2018"
output: ioslides_presentation
df_print: paged
smaller: TRUE
---

```{r setup, include=FALSE}
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, fig.asp = 0.5, fig.height=5)

# Libraries
library(knitr)
library(tidyverse)
library(readxl)
library(arm)
library(raster)

# Theme for ggplot
theme_set(theme_classic()) 

# Load data
dat <- read_xlsx("Data/Daten_Komplett.xlsx")
spec <- dat %>% 
  group_by(Datum_Zahl, Uhrzeit_St, Besucher, Sektor, Art) %>% 
  summarise(Ind = n())
we <- dat %>% filter(Art == "BV")
```


## Research questions
- Ar there differences in species numbers and number of white-eyes in the different sectors
- Is there a change over time (season or daytime)
- Is there a response to the number of visits

## Data
- Number of Withe-Eye individuals: `r length(unique(we$Individuum))`
- Number of species: `r length(unique(spec$Art))`
- Number of sampling days: `r length(unique(dat$Datum_Zahl))`

## Number of recorded species
```{r}
res <- dat %>% 
  group_by(Datum_Zahl) %>% 
  summarise(
    Anz_Arten = n_distinct(Art),
    Anz_WE = n_distinct(Individuum),
    Anz_Sektor = n_distinct(Sektor)
    )

ggplot(res, aes(x = Datum_Zahl, y = Anz_Arten)) +
  geom_point() + 
  geom_line() + 
  ylim(c(0, NA)) +
  labs(x = "Julian Day", y = "Number of species")
```

## Number of recorded White-Eyes
```{r}
ggplot(res, aes(x = Datum_Zahl, y = Anz_WE)) +
  geom_point() + 
  geom_line() + 
  ylim(c(0, NA)) +
  labs(x = "Julian Day", y = "Number of recorded White-Eyes")
```

## Number of sectors with records
```{r}
ggplot(res, aes(x = Datum_Zahl, y = Anz_Sektor)) +
  geom_point() + 
  geom_line() + 
  ylim(c(0, NA)) +
  labs(x = "Julian Day", y = "Number of sectors with records")
```

## Numer of White-Eyes across sectors
```{r}
res <- dat %>% 
  group_by(Datum_Zahl, Sektor) %>% 
  summarise(
    Anz_WE = n_distinct(Individuum)
    )
boxplot(Anz_WE ~ Sektor, data = res, ylim = c(0, 15),
        xlab = "Sector", ylab = "Numbner of recorded White-Eyes")
```

## Numer of Species across sectors
```{r}
res <- spec %>% 
  group_by(Datum_Zahl, Sektor) %>% 
  summarise(
    Anz_Arten = n_distinct(Art)
    )
boxplot(Anz_Arten ~ Sektor, data = res, ylim = c(0, 20),
        xlab = "Sector", ylab = "Numbner of recorded Species")
```

- Some sectors seem to be prefered over others.

## Numer of White-Eyes across hours
```{r}
res <- we %>% 
  group_by(Datum_Zahl, Uhrzeit_St) %>% 
  summarise(
    Anz_WE = n_distinct(Individuum)
    )
boxplot(Anz_WE ~ Uhrzeit_St, data = res, ylim = c(0, 15),
        xlab = "hour of the day", ylab = "Numbner of recorded White-Eyes")
```

## Numer of species across hours
```{r}
res <- spec %>% 
  group_by(Datum_Zahl, Uhrzeit_St) %>% 
  summarise(
    Anz_Species = n_distinct(Art)
    )
boxplot(Anz_Species ~ Uhrzeit_St, data = res, ylim = c(10, 25),
        xlab = "hour of the day", ylab = "Numbner of recorded Species")
```

## Interaction between species?
- How can we test that?
- Based on simulations?



